---
title: "Developing Data Products Course Project"
author: "Tiago Henriques"
date: "29/07/2018"
output:
  ioslides_presentation:
    smaller: true
    widescreen: true
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Project description

The goal of this project is to write a shiny application with associated supporting documentation.

The loaded data was retrieved from this website: http://ourairports.com/data/. The file name is "airports.csv" and contains a lot of information about airports around the world.

For the purpose of this analysis, the data was filtered in order to contain information about the United States only.

```{r, echo=FALSE}
df <- read.csv("/Users/anabarbosa/Downloads/airports.csv", sep = ",", header = TRUE)

df_filtered <- df[,c("type","name","latitude_deg", "longitude_deg", "iso_country")]

df_filtered <- df_filtered[df_filtered$iso_country == "US", ]
df_filtered <- df_filtered[(df_filtered$type == "large_airport" | df_filtered$type == "medium_airport"), ]


df_filtered <- df_filtered[complete.cases(df_filtered), ]

df_filtered$name <- as.character(df_filtered$name)

colnames(df_filtered)[3] <- "lat"
colnames(df_filtered)[4] <- "lon"

```



```{r}
summary(df_filtered)
```


## The application

The application allows the user to select the size of the airport (medium, large) in the United States. The location of the airports is mapped and hover shows the airport name and its size.

The shiny application can be found in the following link:  https://anabarbosa90.shinyapps.io/USAairports/

The shiny application should open in the browser. By checking the input boxes, the type of airport can be selected and will be presented in a map. This map can be zoomed in to show the name of those airports.


## Code for the UI

```{r, eval=FALSE, echo=TRUE}
library(shiny)
library(leaflet)

# Define UI for application that draws a map
shinyUI(fluidPage(
  
  # Application title
  titlePanel("Airports in the USA"),

  sidebarLayout(
    sidebarPanel(
       checkboxGroupInput("airport_choose", label = "Choose a type of airport",
                          choices = c("medium_airport","large_airport"))
    ),
    
    # Show a map
    mainPanel(
       leafletOutput("airportPlot")
    )
  )
))

```

## Code for the shiny server

```{r, eval=FALSE, echo=TRUE}
# Define server logic
shinyServer(function(input, output, session) {
   
  #data manipulation
  
  data_1 <- reactive({df_filtered[df_filtered$type %in% 
                                    input$airport_choose,]})
  
  output$airportPlot <- renderLeaflet({
  data_1() %>% leaflet %>% addTiles() %>% setView(-98.35, 39.7,
                                                  zoom = 4) %>%
      addCircleMarkers(clusterOptions = markerClusterOptions(), 
                       data = data_1(), 
                       lng = ~ lon, lat = ~ lat, 
                       popup = paste("Airport name:", df_filtered$name,
                                     "<br>","Size:", data_1()$type))
    })
  
})
```

