---
title: "Developing Data Products Peer Assignment week 3"
author: "Tiago Henriques"
date: "29/07/2018"
output: ioslides_presentation
---

## Goal

The goal of this project is to create a web page presentation using R Markdown that features a plot created with Plotly. 


## Data

The loaded data was retrieved from this website: http://ourairports.com/data/. The file name is "airports.csv" and contains a lot of information about airports around the world.

For the purpose of this analysis, the data was filtered in order to contain information about large airports only.


```{r cars, echo = FALSE, warning=FALSE}
df <- read.csv("/Users/anabarbosa/Downloads/airports.csv", sep = ",", header = TRUE)

df_filtered <- df[,c("type","name","latitude_deg", "longitude_deg", "iso_country")]

#table(df_filtered$type)

#df_filtered <- df_filtered[df_filtered$iso_country == "US", ]

#df_filtered <- df_filtered[(df_filtered$type == "large_airport" | df_filtered$type == "medium_airport"), ]

#df_filtered <- df_filtered[(df_filtered$type == "large_airport"), ]


df_filtered <- df_filtered[complete.cases(df_filtered), ]

df_filtered$name <- as.character(df_filtered$name)

colnames(df_filtered)[3] <- "lat"
colnames(df_filtered)[4] <- "lon"


data_1 <- df_filtered[df_filtered$type %in% c("small_airport", "medium_airport"),]

```

## Large Airports around the world

```{r, echo=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(plotly))


plot_geo(df_filtered, lat = ~lat, lon = ~lon) %>% add_markers(text = ~name, color= toRGB('red'))

```

