---
title: "Developing Data Products - Peer Assignment 1"
author: "Tiago Henriques"
date: "29/07/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The loaded data was retrieved from this website: http://ourairports.com/data/. The file name is "airports.csv"
## Load libraries

```{r}
library(leaflet)
```

## Load data

Load the CSV file containing the data about all the airports in the world. Filter the dataframe by the type of airport, keeping only small, medium and large airports.

```{r}
df <- read.csv("/Users/anabarbosa/Downloads/airports.csv", sep = ",", header = TRUE)

df_filtered <- df[,c("type","name","latitude_deg", "longitude_deg")]

table(df_filtered$type)

df_filtered <- df_filtered[(df_filtered$type == "large_airport" | df_filtered$type == "medium_airport") | df_filtered$type == "small_airport", ]

colnames(df_filtered)[3] <- "latitude"
colnames(df_filtered)[4] <- "longitude"

```


## Create map


```{r}

pal <- colorFactor(
  palette = 'Blues',
  domain = df_filtered$type
)

map <- df_filtered %>% leaflet() %>%
  addTiles() %>%
  addCircleMarkers(clusterOptions = markerClusterOptions(), data = df_filtered, lng = ~ longitude, lat = ~ latitude, popup = paste("Airport name:", df_filtered$name, "<br>",
                           "Size:", df_filtered$type), color = ~pal(type),
    stroke = FALSE, fillOpacity = 0.5)
  
map
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
